\begingroup
\renewcommand{\section}[2]{\Anonchapter{Список использованных источников}\vspace{-1em}}
\begin{thebibliography}{00}

\bibitem{kant}
      Кант,~И. Сочинения в шести томах. Том 3.~/ И. Кант. [Под общ.~ред. В.~Ф.~Асмуса, А.~В.~Гулыги, Т.~И.~Ойзермана.]~--
      Москва~: Мысль, 1964.~--
      799~с.
    
\bibitem{mathforprogrammers}
      Orland,~P. Math for Progammers~: 3D graphics, machine learning, and simulations with Python~/ P. Orland.~--
      Shelter Island, NY~: Manning, 2020.~--
      688~p.~--
      ISBN 978-1617295355.
      
\bibitem{larson}
      Larson,~R. Precalculus~: a concise course~/ R.~Larson, R.~Hostetler~--
      Boston~: Houghton Mifflin, 2007.~--
      656~p.~--
      ISBN 0-618-62719-7.
      
\bibitem{rowellherbert}
      Роуэлл,~Г. Физика~: учебное издание~/ Г.~Роуэлл, С.~Герберт.~--
      Москва~: Просвещение, 1994.~--
      576~с.~--
      ISBN 5-09-002920-2.
      
\bibitem{alekseevabel}
      Алексеев,~В.~Б. Теорема Абеля в задачах и решениях~/ В.~Б.~Алексеев.~--
      Москва~: МЦНМО, 2001.~--
      192~с.~--
      ISBN 5-900916-86-3.
      
\bibitem{bisectionkaw}
      Autar Kaw. Bisection Method of Solving a Nonlinear Equation~: [textbook chapter]~/ Autar K Kaw //
      Textbook: Numerical Methods with Applications.~--
      URL: \underline{\smash{\href{https://nm.mathforcollege.com/mws/gen/03nle/mws\_gen\_nle\_txt\_bisection.pdf}{https://nm.mathforcollege.com/mws/gen/03nle/mws\_gen\_nle\_txt\_bisection.pdf}}}.~--
      Publication date: 15.01.2012.
      
\bibitem{wiki-ellastic-collision}
      Elastic collision~// Wikipedia~: the free encyclopedia.~--
      URL: \underline{\smash{\href{https://en.wikipedia.org/wiki/Elastic\_collision}{https://en.wikipedia.org/wiki/Elastic\_collision}}}
      (дата~обращения: 26.05.2022).
      
\bibitem{mdn-spa}
      SPA (Single-page application)~// MDN Web Docs.~--
      URL: \underline{\smash{\href{https://developer.mozilla.org/en-US/docs/Glossary/SPA}{https://developer.mozilla.org/en-US/docs/Glossary/SPA}}}
      (дата~обращения: 26.05.2022). 
\bibitem{wasm}
      Haas,~A. Bringing the web up to speed with WebAssembly~/
      Andreas Haas, Andreas Rossberg, Derek L. Schuff [et~al.].~--
      DOI~\href{https://doi.org/10.1145/3062341.3062363}{10.1145/3062341.3062363}~//
      In Proceedings of the 38th ACM SIGPLAN Conference on Programming Language Design and Implementation (PLDI 2017).~--
      2017.~--
      P.~185--200.~--
      URL: \underline{\smash{\href{https://dl.acm.org/doi/pdf/10.1145/3062341.3062363}{https://dl.acm.org/doi/pdf/10.1145/3062341.3062363}}}.~--
      Publication date: 14.06.2017.
      
\bibitem{emscripten-about}
      About Emscripten~// Emscripten documentation.~--
      URL: \underline{\smash{\href{https://emscripten.org/docs/introducing\_emscripten/about\_emscripten.html}{https://emscripten.org/docs/introducing\_emscripten/about\_emscripten.html}}}
      (дата~обращения: 26.05.2022).
      
\bibitem{rust-wasm}
      Why Rust and WebAssembly?~// Rust and WebAssembly~: [документация].~--
      URL: \underline{\smash{\href{https://rustwasm.github.io/docs/book/why-rust-and-webassembly.html}{https://rustwasm.github.io/docs/book/why-rust-and-webassembly.html}}}
      (дата~обращения: 27.05.2022).
    
\bibitem{blazor-ru}
      ASP.NET Core Blazor~// ASP.NET Core~: [документация].~--
      URL: \underline{\smash{\href{https://docs.microsoft.com/ru-ru/aspnet/core/blazor}{https://docs.microsoft.com/ru-ru/aspnet/core/blazor}}}
      (дата~обращения: 27.05.2022).
    
\bibitem{fsbolero}
      Getting started~// Bolero: F\# in WebAssembly.~--
      URL: \underline{\smash{\href{https://fsbolero.io/docs/}{https://fsbolero.io/docs/}}}
      (дата~обращения: 27.05.2022). 
\bibitem{wasm-iwantto}
      I want to...~// WebAssembly.~--
      URL: \underline{\smash{\href{https://webassembly.org/getting-started/developers-guide/}{https://webassembly.org/getting-started/developers-guide/}}}
      (дата~обращения: 27.05.2022). 
\bibitem{dsyme-hopl}
      Syme,~D. The early history of F\#~/ Don Syme.~--
      DOI~\href{https://doi.org/10.1145/3386325}{10.1145/3386325}~//
      Proceedings of the ACM on Programming Languages.~--
      2020.~--
      Vol.~4, Iss.~HOPL.~--
      P.~1--58.~--
      URL: \underline{\smash{\href{https://dl.acm.org/doi/pdf/10.1145/3386325}{https://dl.acm.org/doi/pdf/10.1145/3386325}}}.~--
      Publication date: 12.06.2020.
      
\bibitem{typescript-mayorov}
      Майоров, А. TypeScript для PHP-разработчика. Как писать на JavaScript большие приложения и не сойти с ума /
    А. Майоров // Системный администратор. – 2015. – № 7-8(152-153). – С. 95-99. -- EDN \href{https://www.elibrary.ru/UBPAGH}{UBPAGH}.
      
\bibitem{shutov-haskell}
      Шутов, В.~С. Функциональное программирование для решения математических задач
    / В. С. Шутов // Фундаментальные исследования основных направлений технических и физико - математических наук
    : сборник статей Международной научно-практической конференции, Челябинск, 01 июня 2018 года.
    – Челябинск: Общество с ограниченной ответственностью "Аэтерна", 2018. – С. 120-122. -- EDN \href{https://www.elibrary.ru/XPWRYL}{XPWRYL}.
      
\bibitem{camlhistory}
      A History of Caml~// The Caml Language.~--
      URL: \underline{\smash{\href{https://caml.inria.fr/about/history.en.html}{https://caml.inria.fr/about/history.en.html}}}
      (дата~обращения: 27.05.2022). 
\bibitem{ocamlorg}
      OCaml~: [оффициальный сайт].~--
      URL: \underline{\smash{\href{https://ocaml.org/}{https://ocaml.org/}}}
      (дата~обращения: 27.05.2022).
    
\bibitem{yaron2011}
      Minsky,~Y. OCaml for the Masses: Why the next language you learn should be functional~/ Yaron Minsky.~--
      DOI~\href{https://doi.org/10.1145/2030256.2038036}{10.1145/2030256.2038036}~//
      ACM Queue.~--
      2011.~--
      Vol.~9, Iss.~9.~--
      P.~40--49.~--
      URL: \underline{\smash{\href{https://dl.acm.org/doi/pdf/10.1145/2030256.2038036}{https://dl.acm.org/doi/pdf/10.1145/2030256.2038036}}}.~--
      Publication date: 27.09.2011.
      
\bibitem{rwo-prologue}
      Minsky,~Y. Prologue~: Real World OCaml~/
      Yaron Minsky, Anil Madhavapeddy~//
      Real World OCaml~: Functional programming for the masses (2nd~Edition).~--
      URL: \underline{\smash{\href{https://dev.realworldocaml.org/prologue.html}{https://dev.realworldocaml.org/prologue.html}}} (дата~обращения: 25.05.2022).
      
\bibitem{opam}
      OCaml Package Manager~// OPAM.~--
      URL: \underline{\smash{\href{https://opam.ocaml.org/}{https://opam.ocaml.org/}}}
      (дата~обращения: 29.05.2022). 
\bibitem{npmjs}
      npm.~--
      URL: \underline{\smash{\href{https://www.npmjs.com/}{https://www.npmjs.com/}}}
      (дата~обращения: 29.05.2022).~--
      Режим доступа: для зарегистрированных пользователей.
      
\bibitem{crockford}
      Crockford, D. JavaScript: The World's Most Misunderstood Programming Language~/ Douglas Crockford.~--
      2001.~--
      URL: \underline{\smash{\href{https://www.crockford.com/javascript/javascript.html}{https://www.crockford.com/javascript/javascript.html}}}
      (дата~обращения: 29.05.2022).
      
\bibitem{ocamljs-lambda}
      How ocamljs compiles OCaml to Javascript~// [ocamljs~: документация].~--
      URL: \underline{\smash{\href{https://jaked.org/ocamljs/Jscomp.html}{https://jaked.org/ocamljs/Jscomp.html}}}
      (дата~обращения: 29.05.2022). 
\bibitem{rwo-backend}
      Minsky,~Y. The Compiler Backend: Bytecode and Native code~: Real World OCaml~/
      Yaron Minsky, Anil Madhavapeddy~//
      Real World OCaml~: Functional programming for the masses (2nd~Edition).~--
      URL: \underline{\smash{\href{https://dev.realworldocaml.org/compiler-backend.html}{https://dev.realworldocaml.org/compiler-backend.html}}} (дата~обращения: 25.05.2022).
      
\bibitem{vouillon-jsoo}
      Vouillon J. From bytecode to JavaScript: the Js\_of\_ocaml compiler~/
      Jérôme Vouillon, Vincent Balat.~--
  DOI~\href{https://doi.org/10.1002/spe.2187}{10.1002/spe.2187}~//
  Software: Practice and Experience.~--
  2014.~-- Vol.~44, Iss.~8.~-- P.~951--972.~--
  URL: \underline{\smash{\href{https://www.irif.fr/\~balat/publications/vouillon\_balat-js\_of\_ocaml.pdf}{https://www.irif.fr/{\textasciitilde}balat/publications/vouillon\_balat-js\_of\_ocaml.pdf}}}
  (access~date: 30.05.2022).
  
\bibitem{bobzhang-rawlambda}
      Compiling rawlambda output to javascript~: discuss~// GitHub~: js\_of\_ocaml.~--
      URL: \underline{\smash{\href{https://github.com/ocsigen/js\_of\_ocaml/issues/338}{https://github.com/ocsigen/js\_of\_ocaml/issues/338}}}
      (дата~обращения: 28.05.2022). 
\bibitem{rescript-introduction}
      Introduction~// ReScript Language Manual.~--
      URL: \underline{\smash{\href{https://rescript-lang.org/docs/manual/latest/introduction}{https://rescript-lang.org/docs/manual/latest/introduction}}}
      (дата~обращения: 29.05.2022). 
\bibitem{melange}
      Monteiro,~A. On OCaml and the JS platform~/ Antonio Nuno Monteiro.~--
      URL: \underline{\smash{\href{https://anmonteiro.com/2021/03/on-ocaml-and-the-js-platform/}{https://anmonteiro.com/2021/03/on-ocaml-and-the-js-platform/}}}
      (дата~обращения: 29.05.2022).
    
\bibitem{ocaml-wasm}
      Chan, V. Run OCaml in the browser by WebAssembly~/ Vincent Chan.~--
      URL: \underline{\smash{\href{https://okcdz.medium.com/run-ocaml-in-the-browser-by-webassembly-31ce464594c6}{https://okcdz.medium.com/run-ocaml-in-the-browser-by-webassembly-31ce464594c6}}}
      (дата~обращения: 29.05.2022).
      
\bibitem{ocamlverse-libraries}
      Standard Libraries~// OCamlverse.~--
      URL: \underline{\smash{\href{https://ocamlverse.github.io/content/standard\_libraries.html}{https://ocamlverse.github.io/content/standard\_libraries.html}}}
      (дата~обращения: 29.05.2022). 
\bibitem{janestreet-opensource}
      Jane Street Open Source.~--
      URL: \underline{\smash{\href{https://opensource.janestreet.com/}{https://opensource.janestreet.com/}}}
      (дата~обращения: 29.05.2022).
      
\bibitem{rwo-async}
      Minsky,~Y. Concurrent Programming with Async~: Real World OCaml~/
      Yaron Minsky, Anil Madhavapeddy~//
      Real World OCaml~: Functional programming for the masses (2nd~Edition).~--
      URL: \underline{\smash{\href{https://dev.realworldocaml.org/concurrent-programming.html}{https://dev.realworldocaml.org/concurrent-programming.html}}} (дата~обращения: 25.05.2022).
      
\bibitem{vouillon-lwt}
      Vouillon, J. Lwt: a cooperative thread library~/
      Jérôme Vouillon.~--
  DOI~\href{https://doi.org/10.1145/1411304.1411307}{10.1145/1411304.1411307}~//
  ML '08: Proceedings of the 2008 ACM SIGPLAN workshop on ML.~--
  2008.~-- P.~3--12.~--
  URL: \underline{\smash{\href{https://www.irif.fr//\~vouillon/publi/lwt.pdf}{https://www.irif.fr//{\textasciitilde}vouillon/publi/lwt.pdf}}}
  (access~date: 28.05.2022).
  
\bibitem{announcing-async}
      Announcing Async~// Jane Street Tech Blog.~--
      URL: \underline{\smash{\href{https://blog.janestreet.com/announcing-async/}{https://blog.janestreet.com/announcing-async/}}}
      (дата~обращения: 28.05.2022). 
\bibitem{rgrinberg-async}
      Grinberg, R. Abandoning Async~/ Rudi Grinberg.~--
      URL: \underline{\smash{\href{http://rgrinberg.com/posts/abandoning-async/}{http://rgrinberg.com/posts/abandoning-async/}}}
      (дата обращения: 27.05.2022).
    
\bibitem{jsoo-react}
      jsoo-react~// GitHub.~--
      URL: \underline{\smash{\href{https://github.com/ml-in-barcelona/jsoo-react}{https://github.com/ml-in-barcelona/jsoo-react}}}
      (дата~обращения: 29.05.2022). 
\bibitem{elm-architecture}
      The Elm Architecture~: An Introduction to Elm~// Elm~: [документация].~--
      URL: \underline{\smash{\href{https://guide.elm-lang.org/architecture/}{https://guide.elm-lang.org/architecture/}}}
      (дата~обращения: 28.05.2022). 
\bibitem{lexifi-vdom}
      ocaml-vdom~// GitHub.~--
      URL: \underline{\smash{\href{https://github.com/LexiFi/ocaml-vdom}{https://github.com/LexiFi/ocaml-vdom}}}
      (дата~обращения: 28.05.2022). 
\bibitem{janestreet-virtualdom}
      virtual\_dom~// GitHub.~--
      URL: \underline{\smash{\href{https://github.com/janestreet/virtual\_dom}{https://github.com/janestreet/virtual\_dom}}}
      (дата~обращения: 28.05.2022). 
\bibitem{bonsai-history}
      The History of Bonsai.t~// Github~: bonsai.~--
      URL: \underline{\smash{\href{https://github.com/janestreet/bonsai/blob/master/docs/blogs/history.md}{https://github.com/janestreet/bonsai/blob/master/docs/blogs/history.md}}}
      (дата~обращения: 28.05.2022). 
\bibitem{janestreet-bonsai}
      Bonsai~// Jane Street Open Source.~--
      URL: \underline{\smash{\href{https://opensource.janestreet.com/bonsai/}{https://opensource.janestreet.com/bonsai/}}}
      (дата~обращения: 28.05.2022). 
\bibitem{react-book}
      Бэнкс,~A. React и Redux: функциональная веб-разработка~/ А.~Бэнкс, Е.~Порселло.~--
      Санкт-Петербург~: Питер, 2019.~--
      336~с.~--
      ISBN 978-5-4461-0668-4.
    
\bibitem{minsky-incrdom}
      Minsky,~Y. Data Driven UIs, Incrementally~: [доклад]~/ Yaron Minsky~//
      Strange Loop Conference.~--
      2018.~--
      URL: \underline{\smash{\href{https://www.youtube.com/watch?v=R3xX37RGJKE}{https://www.youtube.com/watch?v=R3xX37RGJKE}}}
      (дата~обращения: 27.05.2022).
      
\bibitem{mdn-websocket}
      WebSocket~: Интерфейсы веб API~// MDN Web Docs.~--
      URL: \underline{\smash{\href{https://developer.mozilla.org/ru/docs/Web/API/WebSocket}{https://developer.mozilla.org/ru/docs/Web/API/WebSocket}}}
      (дата~обращения: 28.05.2022). 
\bibitem{dream}
        Dream : Tidy, feature-complete web framework.~--
        URL: \underline{\smash{\href{https://aantron.github.io/dream/}{https://aantron.github.io/dream/}}}
        (дата~обращения: 27.05.2022). 
\bibitem{rwo-testing}
      Minsky,~Y. Testing~: Real World OCaml~/
      Yaron Minsky, Anil Madhavapeddy~//
      Real World OCaml~: Functional programming for the masses (2nd~Edition).~--
      URL: \underline{\smash{\href{https://dev.realworldocaml.org/testing.html}{https://dev.realworldocaml.org/testing.html}}} (дата~обращения: 25.05.2022).
      
\bibitem{rwo-runtime-memory}
      Minsky,~Y. Memory Representation of Values~: Real World OCaml~/
      Yaron Minsky, Anil Madhavapeddy~//
      Real World OCaml~: Functional programming for the masses (2nd~Edition).~--
      URL: \underline{\smash{\href{https://dev.realworldocaml.org/runtime-memory-layout.html}{https://dev.realworldocaml.org/runtime-memory-layout.html}}} (дата~обращения: 25.05.2022).
      
\bibitem{rwo-json}
      Minsky,~Y. Handling JSON Data~: Real World OCaml~/
      Yaron Minsky, Anil Madhavapeddy~//
      Real World OCaml~: Functional programming for the masses (2nd~Edition).~--
      URL: \underline{\smash{\href{https://dev.realworldocaml.org/json.html}{https://dev.realworldocaml.org/json.html}}} (дата~обращения: 25.05.2022).
      
\bibitem{rwo-sexp}
      Minsky,~Y. Data Serialization with S-Expressions~: Real World OCaml~/
      Yaron Minsky, Anil Madhavapeddy~//
      Real World OCaml~: Functional programming for the masses (2nd~Edition).~--
      URL: \underline{\smash{\href{https://dev.realworldocaml.org/data-serialization.html}{https://dev.realworldocaml.org/data-serialization.html}}} (дата~обращения: 25.05.2022).
      
\bibitem{anil-gemma-qcon}
      Madhavapeddy, A. Fast, Flexible and Functional Programming with OCaml~/
      Anil Madhavapeddy, Gemma Gordon~// QCon Software Development Conference.~--
      London, 2018.~--
      URL: \underline{\smash{\href{https://www.infoq.com/presentations/ocaml-browser-iot/}{https://www.infoq.com/presentations/ocaml-browser-iot/}}}
      (access date: 29.05.2022).
    
\bibitem{rwo-platform}
      Minsky,~Y. The OCaml Platform~: Real World OCaml~/
      Yaron Minsky, Anil Madhavapeddy~//
      Real World OCaml~: Functional programming for the masses (2nd~Edition).~--
      URL: \underline{\smash{\href{https://dev.realworldocaml.org/platform.html}{https://dev.realworldocaml.org/platform.html}}} (дата~обращения: 25.05.2022).
      
\bibitem{bulma-vs-bootstrap}
      An alternative to Bootstrap~// Bulma~: [документация].~--
      URL: \underline{\smash{\href{https://bulma.io/alternative-to-bootstrap/}{https://bulma.io/alternative-to-bootstrap/}}}
      (дата~обращения: 28.05.2022). 
\bibitem{wiki-mlmodules}
      Язык модулей ML~// Википедия~: свободная энциклопедия.~--
      URL: \underline{\smash{\href{https://ru.wikipedia.org/wiki/Язык\_модулей\_ML}{https://ru.wikipedia.org/wiki/Язык\_модулей\_ML}}}
      (дата~обращения: 28.05.2022). 
\bibitem{functor-driven}
    Radanne,~G. Programming Unikernels in the Large via Functor Driven Development~/ Gabriel Radanne, Thomas Gazagnaire, Anil Madhavapeddy [et~al.].~--
    2019.~--
    arXiv \href{https://arxiv.org/abs/1905.02529}{1905.02529}.~--
    URL: \underline{\smash{\href{https://arxiv.org/pdf/1905.02529.pdf}{https://arxiv.org/pdf/1905.02529.pdf}}}.~--
    Publication date: 07.05.2019.
    
\bibitem{intftrick}
    Ferguson,~C. The \_intf trick / Craig Ferguson.~--
            URL: \underline{\smash{\href{https://www.craigfe.io/posts/the-intf-trick}{https://www.craigfe.io/posts/the-intf-trick}}}
            (дата~обращения: 27.05.2022).
    
\bibitem{fprog-adt}
      Душкин,~Р. Алгебраические типы данных и их использование в программировании~/
      Р. Душкин~// Практика функционального программирования~: журнал~--
      2009.~--
      выпуск~2.~--
      С.~49--60.~--
      URL: \underline{\smash{\href{https://www.fprog.ru/2009/issue2/practice-fp-2-compact.pdf}{https://www.fprog.ru/2009/issue2/practice-fp-2-compact.pdf}}}
      (дата~обращения: 29.05.2022).
      
\bibitem{rwo-gadt}
      Minsky,~Y. GADTs~: Real World OCaml~/
      Yaron Minsky, Anil Madhavapeddy~//
      Real World OCaml~: Functional programming for the masses (2nd~Edition).~--
      URL: \underline{\smash{\href{https://dev.realworldocaml.org/gadts.html}{https://dev.realworldocaml.org/gadts.html}}} (дата~обращения: 25.05.2022).
      
\bibitem{mdnsvgtag}
      <svg>~: SVG element reference~// MDN Web Docs.~--
      URL: \underline{\smash{\href{https://developer.mozilla.org/en-US/docs/Web/SVG/Element/svg}{https://developer.mozilla.org/en-US/docs/Web/SVG/Element/svg}}}
      (дата~обращения: 28.05.2022). 
\bibitem{mdn-wheel}
      Element: wheel event~: Web APIs~// MDN Web Docs.~--
      URL: \underline{\smash{\href{https://developer.mozilla.org/en-US/docs/Web/API/Element/wheel\_event}{https://developer.mozilla.org/en-US/docs/Web/API/Element/wheel\_event}}}
      (дата~обращения: 28.05.2022). 
\bibitem{jsoo-issue-1272}
      Wheel event bindings~: feature request~// GitHub~: js\_of\_ocaml.~--
      URL: \underline{\smash{\href{https://github.com/ocsigen/js\_of\_ocaml/issues/1272}{https://github.com/ocsigen/js\_of\_ocaml/issues/1272}}}
      (дата~обращения: 28.05.2022). 
\bibitem{poolpi}
      Galperin.~G. Playing pool with π (the number π from a billiard point of view)~/
      G.~Galperin.~--
  DOI~\href{https://doi.org/10.1070/RD2003v008n04ABEH000252}{10.1070/RD2003v008n04ABEH000252}~//
  Regualar and Chaotic Dynamics.~--
  2003.~-- Vol.~8, №~4.~-- P.~375--394.~--
  URL: \underline{\smash{\href{https://www.maths.tcd.ie/\~lebed/Galperin. Playing pool with pi.pdf}{https://www.maths.tcd.ie/{\textasciitilde}lebed/Galperin. Playing pool with pi.pdf}}}
  (access~date: 25.05.2022).
  
\bibitem{habrpi}
      Как увидеть π? Нужно швырнуть π в стену~// Habr.~--
      URL: \underline{\smash{\href{https://habr.com/ru/post/533454/}{https://habr.com/ru/post/533454/}}}
      (дата~обращения: 29.05.2022). 
\bibitem{browniankrugosvet}
      БРОУНОВСКОЕ ДВИЖЕНИЕ~// Энциклопедия Кругосвет.~--
        URL: \underline{\smash{\href{https://www.krugosvet.ru/enc/nauka\_i\_tehnika/fizika/BROUNOVSKOE\_DVIZHENIE.html}{https://www.krugosvet.ru/enc/nauka\_i\_tehnika/fizika/}}}
        \underline{\smash{\href{https://www.krugosvet.ru/enc/nauka\_i\_tehnika/fizika/BROUNOVSKOE\_DVIZHENIE.html}{BROUNOVSKOE\_DVIZHENIE.html}}}
        (дата~обращения: 30.05.2022). 
\bibitem{wiki-chapaev}
      Чапаев (игра)~// Википедия~: свободная энциклопедия.~--
      URL: \underline{\smash{\href{https://ru.wikipedia.org/wiki/Чапаев (игра)}{https://ru.wikipedia.org/wiki/Чапаев (игра)}}}
      (дата~обращения: 29.05.2022). 
\bibitem{smeshariki-fandom}
      Смешарики (игра)~// Шарарам вики.~--
      URL: \underline{\smash{\href{https://shararam.fandom.com/wiki/Смешарики\_(игра)}{https://shararam.fandom.com/wiki/Смешарики\_(игра)}}}
      (дата~обращения: 29.05.2022). 
\bibitem{vk-games}
      Игровая платформа~// VK для разработчиков.~--
      URL: \underline{\smash{\href{https://dev.vk.com/games/overview}{https://dev.vk.com/games/overview}}}
      (дата~обращения: 29.05.2022). 
\bibitem{tg-games}
      Gaming Platform~// Telegram Bots~: [документация].~--
      URL: \underline{\smash{\href{https://core.telegram.org/bots/games}{https://core.telegram.org/bots/games}}}
      (дата~обращения: 29.05.2022). 
\bibitem{infoqmulticore}
      OCaml 5 Will Include Multicore Support~// InfoQ.~--
      URL: \underline{\smash{\href{https://www.infoq.com/news/2021/10/ocaml-5-multicore/}{https://www.infoq.com/news/2021/10/ocaml-5-multicore/}}}
      (дата~обращения: 29.05.2022). 
\bibitem{domainslibgithub}
      domainslib~// GitHub.~--
      URL: \underline{\smash{\href{https://github.com/ocaml-multicore/domainslib}{https://github.com/ocaml-multicore/domainslib}}}
      (дата~обращения: 29.05.2022). 

  
  \end{thebibliography}
\endgroup
